A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-07-10 docs/methods/revisions.tex
fixed small statement in revision doc
finished up jcp revisions

\noindent
We thank the reviewers for their reviews.  Below is a summary of the
changes.  The revised manuscript also addresses a typo that was in
equation (10).

@@

\noindent
\comment{In section 3.1, formula 29 is missing a $\Delta s_{j}$}
\begin{itemize}
  \item The arclength term is now included in equation (29).
\end{itemize}

>>>>

\noindent
Dear Eric Darve,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewers for their positive and constructive comments.  The attached
manuscript addresses all the reviewers' comments and the result is what
we believe is a stronger manuscript.  
\\ \\
\noindent
We also note that a few typos from the manuscript's original form have
been addressed.  In particular, a small typo in equation (10) is
resolved and some formatting issues were resolved in the bibliography.
An itemized list of the changes addressing the reviewers' comments are
below.
\\ \\
\noindent
Sincerely,
\\
\noindent
Bryan Quaife and Nick Moore

@@

\noindent
\comment{In section 3.1, formula 29 is missing a $\Delta s_{j}$}
\begin{itemize}
  \item We thank the reviewer for noticing this typo.  The arclength
    term is now included in equation (29).
\end{itemize}
